Results

### 2023-03-30 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
contrasts and ref to suppl

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity.
Descriptive values of each predictor for each condition can be found in table \@ref(tab:TabDescr).
We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \@ref(tab:SupplEffectArousalView) to \@ref(tab:SupplEffectLevView).

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression). 
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see Tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and Figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).

@@

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref(fig:FigSubjEffort)).
Post-hoc test showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing. 
Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).

@@

```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots. Dots represent individual effort ratings placed in 150 qantiles.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))
```

>>>>

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity.
Descriptive values of each predictor for each condition can be found in table \@ref(tab:TabDescr).
We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \@ref(tab:SupplEffectArousalView) to \@ref(tab:SupplEffectLevView and Figures \@ref(fig:SupplFigArousalView) to \@ref(fig:SupplFigLevView) in the [supplement]).

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression). 
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc contrasts, please see Tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and Figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).

@@

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref(fig:FigSubjEffort)).
Post-hoc contrasts showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing. 
Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).

@@

```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots. Dots represent individual effort ratings placed in 150 quantiles.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))
```
